Robust Fault-Tolerant Control and Motion Planning of UAVs and Biped Robots Team System for Search and Rescue Usage

### 2022-11-02 paper/paper.tex
paper, figure descriptions.

\section{Reference Tracking control}
After the reference trajectory $r(t)$ is set, the last step is to design a controller for an agent to track it. To analyze the tracking control problem of UAV model in (\ref{eq:uav}) and robot model in (\ref{eq:robot}) together, we represent them by the same form called agent model through some appropriate variable transformations:
\begin{equation} \label{eq:agent} 
    M(x(t))\ddot{x}(t) + H(x(t),\dot{x}(t)) = u(t)
\end{equation}
where $u(t)\in\mathbb{R}^n$ is control input vector, $x(t)\in\mathbb{R}^n$ is state vector, $M(\cdot)\in\mathbb{R}^{n\times n}$ is inertia matrix, and $H(\cdot, \cdot)\in\mathbb{R}^n$ is non-inertial force vector. The control law is given as:
\begin{equation} \label{eq:control}
    u(t)= M(r(t))(\ddot{r}(t) + u_{fb}(t)) + H(r(t),\dot{r}(t)) 
\end{equation}
where $M(r(t)),\ddot{r}(t),H(r(t),\dot{r}(t))$ are the feedfoward control terms for canceling system nonlinearity, and $u_{fb}(t)$ is the feedback control law for improving system robustness. To make the model more realistic, the following external disturbances encountered in actual scenarios are considered:
\begin{enumerate}
    \item For agent, there exists coupling effect due to co-channel interference in communication between agents \cite{9834947}.
    \item For agent, there exists cyber-attack on communication network between agents and ground station.
    \item For agent, there exists sensor noise.
    \item For UAV, there exists wind disturbance \cite{9075385}.
    \item For robot, there exists ground reaction force \cite{chen2013human}. 
\end{enumerate}
Let $x_{i,j}(t), i=1,2,\dots,N_T, j=1,2,\dots,N_A$ denote the state vector of agents $\alpha_{i,j}$.The coupling term can be represented as \begin{equation} \label{eq:UAV couple}
    \sum_{k = 1, k \neq i}^{N_T}f_{i, 1, k}(x_{i, 1}(t))x_{k, 1}(t)
\end{equation} for UAVs $\alpha_{i, 1}$ and \begin{equation} \label{eq:robot couple}
    \sum_{k = 1, k \neq j'}^{N_A}f_{i, j', k}(x_{i, j'}(t))x_{i, k}(t)
\end{equation} for robots $\alpha_{i, j'}$ where $j'=2,3,...,N_A$ \cite{9834947}.

@@

\textit{UAV:}
The trajectories of reference, state and estimated state are shown in Fig. \ref{fig:UAV, state}. The estimation of actuator fault $f_1(t)\in\mathbb{R}^6$ is shown in Fig. \ref{fig:UAV, fa} where the distubance $d_1(t)$ in $f_1(t)$ is set as $d_1(t) = [100\sin(3t),...,10\sin(3t)]^T + \sum_{k = 1, k \neq i}^{N_T}f_{i, 1, k}(x_{i, 1}(t))x_{k, 1}(t)$, i.e., the non-couple term and the couple term in (\ref{eq:UAV couple}). Let $x_{i, 1}(t) = [x_{i, 1, 1}(t)\mathbin{,}\dots\mathbin{,}x_{i, 1, 6}(t)]^T$, then $f_{i, 1, k}(x_{i, 1}(t)) = diag(x_{i, 1, 1}(t)\mathbin{,}\dots\mathbin{,}x_{i, 1, 6}(t))$. The estimation of sensor fault $f_2(t)$ is shown in Fig. \ref{fig:UAV, fs} where $f_2(t)$ is set as a smoothed square wave as shown in figure. The control effort is shown in Fig. \ref{fig:UAV, control}.
\begin{figure}[htbp]
    \centering
    \includegraphics[scale=.57]{fig/uav (1).png}\caption{The trajectories of reference, state and estimated state of the UAV $\alpha_{i,1}$}%
    \label{fig:UAV, state}
\end{figure}
\begin{figure}[htbp]
    \centering
    \includegraphics[scale=.57]{fig/uav (2).png}\caption{The estimation of actuator fault of the UAV $\alpha_{i,1}$}
    \label{fig:UAV, fa}
\end{figure}
\begin{figure}[htbp]
    \centering
    \includegraphics[scale=.57]{fig/uav (3).png}\caption{The estimation of sensor fault of the UAV $\alpha_{i,1}$}%
    \label{fig:UAV, fs}
\end{figure}
\begin{figure}[htbp]
    \centering
    \includegraphics[scale=.57]{fig/uav (4).png}\caption{The control effort of the UAV $\alpha_{i,1}$}%
    \label{fig:UAV, control}
\end{figure}

\textit{Robot:}
The trajectories of reference, state and estimated state are shown in Fig. \ref{fig:robot, state}.
The estimation of actuator fault $f_1(t)\in\mathbb{R}^{12}$ is shown in Fig. \ref{fig:robot, fa} where the distubance $d_1(t)$ in $f_1(t)$ is set as $d_1(t) = [10\sin(3t),...,10\sin(3t)]^T + \sum_{k = 1, k \neq j'}^{N_A}f_{i, j', k}(x_{i, j'}(t))x_{i, k}(t)$, i.e., the non-couple term and the couple term in (\ref{eq:robot couple}). Let $x_{i, j'}(t) = [x_{i, j', 1}(t)\mathbin{,}\dots\mathbin{,}x_{i, j', 12}(t)]^T$, then $f_{i, j', k}(x_{i, j'}(t)) = diag(x_{i, 1, 1}(t)\mathbin{,}\dots\mathbin{,}x_{i, 1, 12}(t))$.

@@

In Fig. \ref{fig:UAV, state}, the tracking and estimation errors of UAV position and attitude reach steady state wihtin $1$ second. There is a brief jitter when the UAV turns, but it returns quickly to steady state. In Fig. \ref{fig:robot, state} , the tracking and estimation errors of robot joint angles immediately reach and maintain steady under the fault signals. In Fig \ref{fig:UAV, fa} and \ref{fig:robot, fa}, the results show that the actuator fault, i.e., disturbances and feedforward errors, can be effectively estimated. However, in Fig \ref{fig:UAV, fs} and \ref{fig:robot, fs}, the estimation of sensor fault has an overshot phenomenon when there is a large change, but returns to a steady state after about $3$ seconds. In Fig \ref{fig:UAV, control} and \ref{fig:robot, control}, the control effort has high frequency and high amplitude performance at the initial instance due to the high gain characteristic of the robust control, and then maintains the sine wave shape to offset the estimated actuator fault value.
% The transient responses that occur later are caused from fault signals, especially the sensor fault. This can be inferred from the dynamic of the estimation error (\ref{eq:e_tilde}) because the value of the sensor fault affects the value of the estimation error over time $\dot{e}$ not only from the term $\bar{A}$ but also from the term $L\bar{C}$.

>>>>

\section{Reference Tracking control}
After the reference trajectory $r(t)$ is set, the last step is to design a controller for an agent to track it. To analyze the tracking control problem of UAV model in (\ref{eq:uav}) and robot model in (\ref{eq:robot}) together, we represent them by the same form called agent model through some appropriate variable transformations:
\begin{equation} \label{eq:agent} 
    M(x(t))\ddot{x}(t) + H(x(t),\dot{x}(t)) = u(t)
\end{equation}
where $u(t)\in\mathbb{R}^n$ is control input vector, $x(t)\in\mathbb{R}^n$ is state vector, $M(\cdot)\in\mathbb{R}^{n\times n}$ is inertia matrix, and $H(\cdot, \cdot)\in\mathbb{R}^n$ is non-inertial force vector. The control law is given as:
\begin{equation} \label{eq:control}
    u(t)= M(r(t))(\ddot{r}(t) + u_{fb}(t)) + H(r(t),\dot{r}(t)) 
\end{equation}
where $M(r(t)),\ddot{r}(t),H(r(t),\dot{r}(t))$ are the feedfoward control terms for canceling system nonlinearity, and $u_{fb}(t)$ is the feedback control law for improving system robustness. To make the model more realistic, the following external disturbances encountered in actual scenarios are considered:
\begin{enumerate}
    \item For agent, there exists coupling effect due to co-channel interference in communication between agents \cite{9834947}.
    \item For agent, there exists cyber-attack on communication network between agents and ground station.
    \item For agent, there exists sensor noise.
    \item For UAV, there exists wind disturbance \cite{9075385}.
    \item For robot, there exists ground reaction force \cite{chen2013human}. 
\end{enumerate}
Let $x_{i,j}(t), i=1,2,\dots,N_T, j=1,2,\dots,N_A$ denote the state vector of agents $\alpha_{i,j}$.The coupling term can be represented as \begin{equation} \label{eq:UAV couple}
    \sum_{k = 1, k \neq i}^{N_T}h_{i, 1, k}(x_{i, 1}(t))x_{k, 1}(t)
\end{equation} for UAVs $\alpha_{i, 1}$ and \begin{equation} \label{eq:robot couple}
    \sum_{k = 1, k \neq j'}^{N_A}h_{i, j', k}(x_{i, j'}(t))x_{i, k}(t)
\end{equation} for robots $\alpha_{i, j'}$ where $j'=2,3,...,N_A$ \cite{9834947}.

@@

\textit{UAV:}
The trajectories of reference, state and estimated state are shown in Fig. \ref{fig:UAV, state}. The estimation of actuator fault $f_1(t)\in\mathbb{R}^6$ is shown in Fig. \ref{fig:UAV, fa} where the distubance $d_1(t)$ in $f_1(t)$ is set as $d_1(t) = [100\sin(3t),...,10\sin(3t)]^T + \sum_{k = 1, k \neq i}^{N_T}h_{i, 1, k}(x_{i, 1}(t))x_{k, 1}(t)$, i.e., the non-couple term and the couple term in (\ref{eq:UAV couple}). Let $x_{i, 1}(t) = [x_{i, 1, 1}(t)\mathbin{,}\dots\mathbin{,}x_{i, 1, 6}(t)]^T$, then $h_{i, 1, k}(x_{i, 1}(t)) = diag(x_{i, 1, 1}(t)\mathbin{,}\dots\mathbin{,}x_{i, 1, 6}(t))$. The estimation of sensor fault $f_2(t)$ is shown in Fig. \ref{fig:UAV, fs} where $f_2(t)$ is set as a smoothed square wave as shown in figure. The control effort is shown in Fig. \ref{fig:UAV, control}.
\begin{figure}[htbp]
    \centering
    \includegraphics[scale=.57]{fig/uav (1).png}\caption{The trajectories of reference, state and estimated state of the UAV $\alpha_{i,1}$}%
    \label{fig:UAV, state}
\end{figure}
\begin{figure}[htbp]
    \centering
    \includegraphics[scale=.57]{fig/uav (2).png}\caption{The estimation of actuator fault of the UAV $\alpha_{i,1}$}
    \label{fig:UAV, fa}
\end{figure}
\begin{figure}[htbp]
    \centering
    \includegraphics[scale=.57]{fig/uav (3).png}\caption{The estimation of sensor fault of the UAV $\alpha_{i,1}$}%
    \label{fig:UAV, fs}
\end{figure}
\begin{figure}[htbp]
    \centering
    \includegraphics[scale=.57]{fig/uav (4).png}\caption{The control effort of the UAV $\alpha_{i,1}$}%
    \label{fig:UAV, control}
\end{figure}

\textit{Robot:}
The trajectories of reference, state and estimated state are shown in Fig. \ref{fig:robot, state}.
The estimation of actuator fault $f_1(t)\in\mathbb{R}^{12}$ is shown in Fig. \ref{fig:robot, fa} where the distubance $d_1(t)$ in $f_1(t)$ is set as $d_1(t) = [10\sin(3t),...,10\sin(3t)]^T + \sum_{k = 1, k \neq j'}^{N_A}h_{i, j', k}(x_{i, j'}(t))x_{i, k}(t)$, i.e., the non-couple term and the couple term in (\ref{eq:robot couple}). Let $x_{i, j'}(t) = [x_{i, j', 1}(t)\mathbin{,}\dots\mathbin{,}x_{i, j', 12}(t)]^T$, then $h_{i, j', k}(x_{i, j'}(t)) = diag(x_{i, 1, 1}(t)\mathbin{,}\dots\mathbin{,}x_{i, 1, 12}(t))$.

@@

In Fig. \ref{fig:UAV, state}, the tracking and estimation errors of UAV position and attitude reach steady state wihtin $2$ second. There is a brief jitter when the sensor fault signal changes drastically, but it returns quickly to steady state. In Fig. \ref{fig:robot, state}, the tracking and estimation errors of robot joint angles immediately reach and maintain steady under the influence of fault signals. In Fig \ref{fig:UAV, fa} and \ref{fig:robot, fa}, the results show that the actuator fault, i.e., disturbances and feedforward errors, can be effectively estimated. However, in Fig \ref{fig:UAV, fs} and \ref{fig:robot, fs}, the estimation of sensor fault has an overshot phenomenon when there is a large change and returns to a steady state after about $3$ seconds. In Fig \ref{fig:UAV, control} and \ref{fig:robot, control}, the control efforts has high frequency and high amplitude performance at the initial instance due to the high gain characteristic of the robust control. After that, they maintain the sine wave shape to offset the estimated actuator fault value. Besides, it can be seen that the total force $F$ remains constant against gravity in Fig \ref{fig:UAV, control}.
% The transient responses that occur later are caused from fault signals, especially the sensor fault. This can be inferred from the dynamic of the estimation error (\ref{eq:e_tilde}) because the value of the sensor fault affects the value of the estimation error over time $\dot{\tilde{e}}$ not only from the term $\bar{A}$ but also from the term $L\bar{C}$.
